My Cool Title

### 2019-05-05 paper.tex
Added previous work for object detector. Need to add references

\todo{Object detectors}

@@

>>>>

Object detectors can be divided into two main categories that use single-stage and 2-stage methods.  
The two-stage methods use a region proposal approach [ref] where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
They typically reach higher accuracy, but at the cost of more memory and computational resources.\todo{cite}
The Faster-RCNN [ref] is an example of a 2-stage network that uses RPN\todo{what is rpn} for region proposals. 
On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
These methods, such as Single-Shot Detection (SSD) and You Only Look Once (YOLO), typically need less computational resources, but at the cost of lower accuracy.\todo{cite} 
Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
Mobilenet [ref] is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
This leads to model that uses much less memory, but with a small drop in accuracy\todo{cite}.

@@

The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2\todo{cite} for its backbone.
This leads to a more `lightweight' model that has less parameters and requires less memory to perform inference tasks, which makes it suitable for a mobile platform.
